The Astropy Project

### 2017-10-24 main.tex
typo

A set of circular statistical estimators based on \citet{JammalamadakaSengupta}
are implemented in the \package{stats} package.  These functions provide
measurements of the circular mean, variance, and moment.   For all of these
functions, they work with both \texttt{numpy.ndarrays} (assumed to be in
radians) and \texttt{Quantity} objects.  In addition, the package includes
tests for Raleigh Test [XXX], vtest [XXX], and a function to compute the
maximum likelihood estimator for the parameters of the von Mises distribution
[XXX].

>>>>

A set of circular statistical estimators based on \citet{JammalamadakaSengupta}
are implemented in the \package{stats} package.  These functions provide
measurements of the circular mean, variance, and moment.   For all of these
functions, they work with both \texttt{numpy.ndarrays} (assumed to be in
radians) and \texttt{Quantity} objects.  In addition, the package includes
tests for Rayleigh Test [XXX], vtest [XXX], and a function to compute the
maximum likelihood estimator for the parameters of the von Mises distribution
[XXX].
